### 2020-06-30 paper/paper.tex
paper

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Vision and Cognitive Systems Final Project}
\author{\IEEEauthorblockN{Fabio Polito}
\IEEEauthorblockA{\textit{230635@studenti.unimore.it}}
\and
\IEEEauthorblockN{Giordano Costi}
\IEEEauthorblockA{\textit{226934@studenti.unimore.it}}\\
\large{Univerisity of Modena and Reggio Emilia}
\and
\IEEEauthorblockN{Stefano Carretti}
\IEEEauthorblockA{\textit{227250@studenti.unimore.it}}
}
\maketitle

\section{Introduction}
In this paper, we present a method to detect and identify paintings starting from a video taken inside “Galleria Estensi, Modena”.\\
Each frame is processed with image processing techniques in order to localize paintings, rectify distortions, and fetch from the database the corresponding work of art.\\
At the same time, an artificial neural network (YoloV3) detects people, which are localized inside a room of the museum.

\section{Painting Detection}
All frames are exctracted in sequence from the video and processed independently. The followed pipeline is explained afterwards.

\subsection{Preprocessing}
First of all, each frame is converted into black and white and processed with a bilateral filter to remove noise while preserving at the same time the edges.\\
After that, we apply otsu threshold  with the aim to separate the pixels into background and paintings, due to their chromatic difference.

\subsection{Bounding Box detection}
Using the function findContours of OpenCV, we obtain the outlines of the objects in the foreground, among which there will also be the paintings that we are looking for.\\
We then create the bounding box containing this contours and to eliminate the rectangles identified inside the paintings, we keep only the external ones and eliminate those contained within others.\\
Among the remaining bounding boxes, those that are not judged as paintings by an SVM model, will get discarded.

\subsection{SVM}
To classify the ROI proposed by the previous pipeline, an SVM model is been trained.\\
The algorithm takes as input the concatenation of the three histograms, one for each color plane.\\
The training dataset is composed of 1025 instances taken from bounding boxes derivate from the videos inside the museum and manually labeled.
409 of the samples are labeled as holding a painting and 604 as inaccurate bounding box.\\
A radial basis function kernel is been exploited for the classification.
The model returns False if the rectangle doesn't contain a painting and True if it does.

\subsection{Precision boosting and paintings segmentation}
To obtain a better segmentation within each bounding box we apply a further refinement of the images.\\
Observing the low light in the videos that were provided to us, the paintings\\
are significantly darker compared to their frame and do not correspond to the brightness of the paintings in the database. This leads to poor precision in the retrieval step. To cope with this problem, the brightness component is increased for each previously found bounding box.\\
Afterward, by transforming its format from BGR to HSV and then applying the otsu threshold again, we are able to obtain a more precise distinction between painting and frame/background, which will then be used during the retrieval and rectification steps.

\section{Painting Retrieval}
For the retrieval of the paintings situated in the database we use an approach based on feature detection algorithms.\\ 
After consulting a paper that performs a comparative analysis between the most well known algorithms ~\cite{b1} to get a general idea of the strengths and weaknesses of the different methods available to us, we carried out some experiments focusing on SIFT, AKAZE and ORB.\\
The results obtained made us opt for ORB, because overall it gave us more precise results than AKAZE and, unlike SIFT, it’s free of charge, therefore usable without fees in a possible commercial application.\\
To save time, the key points of the paintings in the database have been previously calculated and stored using the pickle module [link pickle documentation].\\
It implements binary protocols for serializing and de-serializing a Python object structure.\\
This data is loaded only once during the launch of the program.
The key points are computed from the bounding boxes detected by the previously described pipeline and afterward, to determine the best matches, the ratio test proposed by D. Lowe in the SIFT paper is performed[Reference to the sift paper].\\
This measure is obtained by comparing the distance of the closest neighbor to that of the second-closest neighbor.\\
This measure performs well because correct matches need to have the closest neighbor significantly closer than the closest incorrect match to achieve reliable matching.\\
For false matches, there will likely be a number of other false matches within similar distances due to the high dimensionality of the feature space.\\
In our implementation we reject all matches in which the distance ratio is greater than 0.75.\\
This allows us to keep the number of correctly retrieved paintings still high but at the same time to decrease the number of false positive.
A ranking with the 5 best matches found is then created and saved to a CSV file to show the results.\\
To understand if the painting is actually recognized among those in the DB, the average of the key points matched among the best 5 ranked is calculated and, if the first one differs from it for more than significant value, it is considered as correct and shown on the interface.

\section{Painting Rectification}
\subsection{Four points transform}
On the contour found with the techniques described in \textbf{Precision boosting and paintings segmentation} is applied the function approxPolyDP from OpenCV to approximate it to a polygonal curve.\\
If the shape returned has four vertices we can assume that the process has found a rectangular painting.\\
Given the four points, we are able to estimate the homography and apply the transformation to rectify the painting.\\
To calculate the aspect ratio for the projected rectangle we use an implementation based on this paper [] which derives the equations assuming a pinhole camera model.\\
This pipeline is applied to the paintings that don't get a match on the database.

\subsection{alignImages}
Not all the paintings inside the museum have a rectangular shape. This means that the approximation found by approxPolyDP does not consist of 4 vertices, making the method just explained impractical.\\
The approach that is used in this case is based on the common keypoints found between the distorted image and the corresponding match in the database.\\
Through ORB feature matching algorithm the key points are computed from each bounding boxes detected by the previous pipeline and subsequently, to determine the best matches between it and the images of the database, the ratio test is used.\\
From them we calculate the homography matrix and
to avoid mismatches, the RANSAC algorithm is exploited.\\
To obtain a better result also the inverse warping algorithm is utilized.

\section{People Detection}
A neural network (YoloV3) is used for people detection.\\
Each video frame is passed through the network tho make inference, and find all bounding boxes containing one of the objects in our classes list.\\
The weights for the network are obtained from an already trained network on COCO[ reference to COCO paper], a famous dataset containing 80 different classes.\\
In our case the only wanted class is the person one, for ease of use the network has not been modified, but from its output will be deleted all the classes with an id different from 0 that is the id of the person class.\\
A little problem has arisen due to the high number of paintings representing persons, in fact the network detect them also inside the paintings, to prevent these false positive we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting.

\section{People Localization}
People Localization

\section{Painting Replacement in the 3D Model}
Painting Replacement in the 3D Model

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} Tareen, Shaharyar Ahmed Khan, and Zahra Saleem. "A comparative analysis of sift, surf, kaze, akaze, orb, and brisk." 2018 International conference on computing, mathematics and engineering technologies (iCoMET). IEEE, 2018.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2020-06-30 ReplacingPaintings3dModel_main.py
3d model screenshots

@@ -94,9 +94,10 @@ def main_3d(img):
     img = cv2.resize(img, (1200, 1000))
     cv2.imshow('after', cv2.resize(img, (800, 650)))
     cv2.waitKey()
+    cv2.imwrite('Paper_Presentation/3DModel/replaced_10.png', img)
     return img
 
 
 if __name__ == '__main__':
-    img = cv2.imread('screenshots_3d_model/screenshot_03.png', cv2.IMREAD_COLOR)
+    img = cv2.imread('screenshots_3d_model/screenshot_10.jpg', cv2.IMREAD_COLOR)
     main_3d(img)

### 2020-06-30 Paper_Presentation/paper/paper.tex
paper updates

--- 2020-06-30 paper/paper.tex
@@
 This measure performs well because correct matches need to have the closest neighbor significantly closer than the closest incorrect match to achieve reliable matching.\\
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.8\columnwidth]{../Orb_matches/match3.png}}
+\caption{Orb matches}
+\label{fig}
+\end{figure}
+
 For false matches, there will likely be a number of other false matches within similar distances due to the high dimensionality of the feature space.\\
@@
 
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.8\columnwidth]{../detection_and_rectification/top_association_vid05.png}}
+\caption{Painting detection and rectification}
+\label{fig}
+\end{figure}
+
 \subsection{alignImages}
@@
 A neural network (YoloV3) is used for people detection.\\
-Each video frame is passed through the network tho make inference, and find all bounding boxes containing one of the objects in our classes list.\\
+At inference time each video frame is passed through the network that find all bounding boxes containing one of the objects in our classes list.\\
 The weights for the network are obtained from an already trained network on COCO[ reference to COCO paper], a famous dataset containing 80 different classes.\\
 In our case the only wanted class is the person one, for ease of use the network has not been modified, but from its output will be deleted all the classes with an id different from 0 that is the id of the person class.\\
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.8\columnwidth]{../people_detection/paint_and_person.png}}
+\caption{People detection}
+\label{fig}
+\end{figure}
+
 A little problem has arisen due to the high number of paintings representing persons, in fact the network detect them also inside the paintings, to prevent these false positive we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting.
 
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.8\columnwidth]{../people_detection/people_error.png}}
+\caption{People detection error}
+\label{fig}
+\end{figure}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.8\columnwidth]{../people_detection/people_error_fixed.png}}
+\caption{People detection error fixed}
+\label{fig}
+\end{figure}
+
 \section{People Localization}
-People Localization
+Starting from a previously detected and retrieved painting from the database, we search the corresponding room in csv file, then a little red dot is printed on the museum image map.
+With this method we assume that all the painting detected and the persons are in the same room.
+Moreover the localization will work only if the painting matched is considered safe that means the painting need to have a good level of matches, otherwise localization is not active.
 
 \section{Painting Replacement in the 3D Model}
-Painting Replacement in the 3D Model
+the pipeline followed to accomplish this task is similar to the one explained before with a little difference.
+we start directly with the hsv version of the image taken as input (a screenshot from the 3d model); then we apply Otsu threshold, followed by noise removal thanks to opening or closing process, keeping the one that maximizes the number of contours found.
+At this point we loop over each contour and find an approximation of itself with approxPolyDP; if the approximation has a shape described by 4 vertices, we estimate keypoints with orb and fetch the corresponding image from the database.
+Once this is done, if the image fetched is judged as a good match, we align that image with respect to the screenshot’s image plane and superimpose the result on the input image.
+what is worth to mention is that the alignment function that we use in this process is the same of the main pipeline of painting rectification.
+this function in fact takes as input two images and project the first one on the plane of the second.
+if the second image is a painting fetched from the database, it means that the first image is rectified; if instead the second image is a painting coming from a frame/screenshot, it means that we want to distort an image in order to match the perspective of that painting.
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+\section{Metrics and Precision}
+To calculate the precision of the presented method we took almost 10 random frame for 6 different videos and labeled all the paintings by hand using a tool for labeling (normally used for yolo labels).
+Then with a custom code we calculated precision recall… comparing hand made labels with automatically generated ones.
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.8\columnwidth]{../Labeling_precision_metrics/Precision_Labeling.png}}
+\caption{labeling.}
+\label{fig}
+\end{figure}
 
 \begin{table}[htbp]
-\caption{Table Type Styles}
+\caption{Metrics Table}
 \begin{center}
@@
 \end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
 
@@
 \end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
 

### 2020-06-30 Paper_Presentation/paper/paper.tex
paper updates 2

@@
 At the same time, an artificial neural network (YoloV3) detects people, which are localized inside a room of the museum.
+
+\section{Related Works}
+To remove camera noise but maintains the contours a  Bilateral filter is used.
+C.
+Tomasi and R.
+Manduchi, "Bilateral filtering for gray and color images," Sixth International Conference on Computer Vision (IEEE Cat.
+No.98CH36271), Bombay, India, 1998, pp.
+839-846, doi: 10.1109/ICCV.1998.710815.
+
+OTSU is an automatic thresholding method widely used when the numbers of pixels in each class are close to each other.
+J.
+Zhang and J.
+Hu, "Image Segmentation Based on 2D Otsu Method with Histogram Analysis," 2008 International Conference on Computer Science and Software Engineering, Hubei, 2008, pp.
+105-108, doi: 10.1109/CSSE.2008.206.
+
+Opencv Find Counturs function is been used to find counturs in a previouslly modified frame in order to detect painting
+Suzuki, S., and Be, K.
+(1985).
+Topological structural analysis of digitized binary images by border following.
+Computer Vision, Graphics, and Image Processing 30, 32–46.
+doi:10.1016/0734-189X(85)90016-7.
+
+The functions approxPolyDP approximate a curve or a polygon with another curve/polygon with less vertices so that the distance between them is less or equal to the specified precision.
+It uses the Douglas-Peucker algorithm
+
+ORB E.
+Rublee, V.
+Rabaud, K.
+Konolige and G.
+Bradski, "ORB: An efficient alternative to SIFT or SURF," 2011 International Conference on Computer Vision, Barcelona, 2011, pp.
+2564-2571, doi: 10.1109/ICCV.2011.6126544.
+
+YoloV3 is a famous neural network for fast object detection, will be used in this paper for people detection
+Redmon, Joseph and Ali Farhadi. “YOLOv3: An Incremental Improvement.” ArXiv abs/1804.02767 (2018): n. pag.
 
@@
 \caption{Orb matches}
-\label{fig}
+\label{fig_Orb_matches}
 \end{figure}
@@
 \caption{Painting detection and rectification}
-\label{fig}
+\label{fig_Painting_detection_and_rectification}
 \end{figure}
@@
 \caption{People detection}
-\label{fig}
+\label{fig_People_detection}
 \end{figure}
@@
 \caption{People detection error}
-\label{fig}
+\label{fig_People_detection_error}
 \end{figure}
@@
 \caption{People detection error fixed}
-\label{fig}
+\label{fig_People_detection_error_fixed}
 \end{figure}
@@
 \section{Painting Replacement in the 3D Model}
-the pipeline followed to accomplish this task is similar to the one explained before with a little difference.
+The pipeline followed to accomplish this task is similar to the one explained before with a little difference.
 we start directly with the hsv version of the image taken as input (a screenshot from the 3d model); then we apply Otsu threshold, followed by noise removal thanks to opening or closing process, keeping the one that maximizes the number of contours found.
@@
 Once this is done, if the image fetched is judged as a good match, we align that image with respect to the screenshot’s image plane and superimpose the result on the input image.
-what is worth to mention is that the alignment function that we use in this process is the same of the main pipeline of painting rectification.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.8\columnwidth]{../screenshots_3d_model/screenshot_01.jpg}}
+\caption{3dmodel}
+\label{fig_3d_model}
+\end{figure}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.8\columnwidth]{../screenshots_3d_model/screenshot_03.png}}
+\caption{3d model 2}
+\label{fig_3d_model_2}
+\end{figure}
+
+What is worth to mention is that the alignment function that we use in this process is the same of the main pipeline of painting rectification.
 this function in fact takes as input two images and project the first one on the plane of the second.
@@
 \centerline{\includegraphics[width=0.8\columnwidth]{../Labeling_precision_metrics/Precision_Labeling.png}}
-\caption{labeling.}
-\label{fig}
+\caption{labeling}
+\label{fig_labeling}
 \end{figure}
@@
 
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+\section*{Discussions}
+L’approccio seguito si fonda sull’assunzione che nel video in questione sia presente una buona differenza cromatica tra background e paintings.
+nel caso questa condizione non sia verificata, come nel caso di una inquadratura più ampia comprendente non solo quadri e parete ma anche corridoio ad esempio, otsu non riesce a dividere correttamente quadri da background e le performance della detection calano.
+cronologia degli approcci testati
+inizialmente si è pensato di utilizzare Canny, preceduto da una rimozione iniziale di rumore prodotta dal bilateral filter, per trovare i bordi su cui applicare findContours.
+i risultati non erano del tutto soddisfacenti in quanto spesso i contorni prodotti da canny non individuavano con precisione il quadro.
+abbiamo quindi optato per una soluzione basata sul thresholding dell’immagine rgb, che come già spiegato in precedenza è seguita da un raffinamento effettuato a livello hsv.
+Si è anche testato un metodo basata solo su immagini hsv, che ha rivelato essere molto performante in certe situazioni (in ogni frame vi è una chiara distinzione tra quadro e background) ma meno stabile rispetto al metodo precedentemente esposto.
 
 \section*{References}
-
 Please number citations consecutively within brackets \cite{b1}. The 

### 2020-06-30 Paper_Presentation/paper/paper.tex
paper updates 3

@@
 \section{Related Works}
-To remove camera noise but maintains the contours a  Bilateral filter is used.
-C.
-Tomasi and R.
-Manduchi, "Bilateral filtering for gray and color images," Sixth International Conference on Computer Vision (IEEE Cat.
-No.98CH36271), Bombay, India, 1998, pp.
-839-846, doi: 10.1109/ICCV.1998.710815.
-
-OTSU is an automatic thresholding method widely used when the numbers of pixels in each class are close to each other.
-J.
-Zhang and J.
-Hu, "Image Segmentation Based on 2D Otsu Method with Histogram Analysis," 2008 International Conference on Computer Science and Software Engineering, Hubei, 2008, pp.
-105-108, doi: 10.1109/CSSE.2008.206.
-
-Opencv Find Counturs function is been used to find counturs in a previouslly modified frame in order to detect painting
-Suzuki, S., and Be, K.
-(1985).
-Topological structural analysis of digitized binary images by border following.
-Computer Vision, Graphics, and Image Processing 30, 32–46.
-doi:10.1016/0734-189X(85)90016-7.
-
-The functions approxPolyDP approximate a curve or a polygon with another curve/polygon with less vertices so that the distance between them is less or equal to the specified precision.
+To remove camera noise but maintains the contours a  Bilateral filter\cite{b1} is used.
+OTSU\cite{b2} is an automatic thresholding method widely used when the numbers of pixels in each class are close to each other.
+Opencv Find Counturs\cite{b3} function is been used to find counturs in a previouslly modified frame in order to detect painting
+The functions approxPolyDP\cite{b4} approximate a curve or a polygon with another curve/polygon with less vertices so that the distance between them is less or equal to the specified precision.
 It uses the Douglas-Peucker algorithm
-
-ORB E.
-Rublee, V.
-Rabaud, K.
-Konolige and G.
-Bradski, "ORB: An efficient alternative to SIFT or SURF," 2011 International Conference on Computer Vision, Barcelona, 2011, pp.
-2564-2571, doi: 10.1109/ICCV.2011.6126544.
-
-YoloV3 is a famous neural network for fast object detection, will be used in this paper for people detection
-Redmon, Joseph and Ali Farhadi. “YOLOv3: An Incremental Improvement.” ArXiv abs/1804.02767 (2018): n. pag.
+ORB\cite{b5} is a feature detection algorithm like SIFT while being almost two orders of magnitude faster.
+YoloV3 \cite{b5}  is a famous neural network for fast object detection, will be used in this paper for people detection
 
@@
 
-\section*{Discussions}
-L’approccio seguito si fonda sull’assunzione che nel video in questione sia presente una buona differenza cromatica tra background e paintings.
-nel caso questa condizione non sia verificata, come nel caso di una inquadratura più ampia comprendente non solo quadri e parete ma anche corridoio ad esempio, otsu non riesce a dividere correttamente quadri da background e le performance della detection calano.
-cronologia degli approcci testati
-inizialmente si è pensato di utilizzare Canny, preceduto da una rimozione iniziale di rumore prodotta dal bilateral filter, per trovare i bordi su cui applicare findContours.
-i risultati non erano del tutto soddisfacenti in quanto spesso i contorni prodotti da canny non individuavano con precisione il quadro.
-abbiamo quindi optato per una soluzione basata sul thresholding dell’immagine rgb, che come già spiegato in precedenza è seguita da un raffinamento effettuato a livello hsv.
-Si è anche testato un metodo basata solo su immagini hsv, che ha rivelato essere molto performante in certe situazioni (in ogni frame vi è una chiara distinzione tra quadro e background) ma meno stabile rispetto al metodo precedentemente esposto.
+\section{Discussions}
+Our approach is based on the assumption that input videos contain a relevant chromatic difference between paintings and background.
+when this assumption doesn’t occur, for example in the case of a wider shot comprising hallway too, otsu doesn’t manage to correctly differentiate paintings from the rest, which leads to worse performances.
 
-\section*{References}
+\subsection{tested methods history}
+At the beginning the idea was to use Canny, preceded by an initial noise removal obtained by bilateral filter, in order to find the edges on which to apply findContours opencv function.
+The results were not entirely satisfactory as the outlines often produced by canny did not accurately identify the picture.
+We therefore opted for a solution based on the thresholding of the RGB image, which as already explained above is followed by a refinement carried out at the hsv level.
+A method based only on hsv images was also tested, which revealed to be very performing in certain situations (in each frame there is a clear distinction between picture and background) but less stable than the previously exposed method.
+It was then necessary to face the fact that each method, being based solely on image processing techniques, produced many false positives.
+The simplest way, according to which only bounding boxes containing a painting that had been matched on the database should have been shown, was discarded due to the limited database.
+many correctly identified paintings were in fact discarded because they were not present in the database.
+The solution adopted was to train an svm with the goal to classify what is a painting and what is not.
+
+\section{References}
 Please number citations consecutively within brackets \cite{b1}. The 
@@
 \begin{thebibliography}{00}
-\bibitem{b1} Tareen, Shaharyar Ahmed Khan, and Zahra Saleem.
-"A comparative analysis of sift, surf, kaze, akaze, orb, and brisk." 2018 International conference on computing, mathematics and engineering technologies (iCoMET).
-IEEE, 2018.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+\bibitem{b1} C.
+Tomasi and R.
+Manduchi, "Bilateral filtering for gray and color images," Sixth International Conference on Computer Vision (IEEE Cat.
+No.98CH36271), Bombay, India, 1998, pp.
+839-846, doi: 10.1109/ICCV.1998.710815..
+\bibitem{b2} J.
+Zhang and J.
+Hu, "Image Segmentation Based on 2D Otsu Method with Histogram Analysis," 2008 International Conference on Computer Science and Software Engineering, Hubei, 2008, pp.
+105-108, doi: 10.1109/CSSE.2008.206.
+\bibitem{b3}Suzuki, S., and Be, K.
+(1985).
+Topological structural analysis of digitized binary images by border following.
+Computer Vision, Graphics, and Image Processing 30, 32–46.
+doi:10.1016/0734-189X(85)90016-7.
+\bibitem{b4} 
+\bibitem{b5} E.
+Rublee, V.
+Rabaud, K.
+Konolige and G.
+Bradski, "ORB: An efficient alternative to SIFT or SURF," 2011 International Conference on Computer Vision, Barcelona, 2011, pp.
+2564-2571, doi: 10.1109/ICCV.2011.6126544.
+\bibitem{b6}Redmon, Joseph and Ali Farhadi. “YOLOv3: An Incremental Improvement.” ArXiv abs/1804.02767 (2018): n. pag.
 \end{thebibliography}

### 2020-06-30 Paper_Presentation/paper/paper.tex
metrics table

@@
 \end{figure}
+\bigskip
 
@@
 The pipeline followed to accomplish this task is similar to the one explained before with a little difference.
-we start directly with the hsv version of the image taken as input (a screenshot from the 3d model); then we apply Otsu threshold, followed by noise removal thanks to opening or closing process, keeping the one that maximizes the number of contours found.
+It starts directly with the hsv version of the image taken as input (a screenshot from the 3d model); then we apply Otsu threshold, followed by noise removal thanks to opening or closing process, keeping the one that maximizes the number of contours found.
 At this point we loop over each contour and find an approximation of itself with approxPolyDP; if the approximation has a shape described by 4 vertices, we estimate keypoints with orb and fetch the corresponding image from the database.
@@
 What is worth to mention is that the alignment function that we use in this process is the same of the main pipeline of painting rectification.
-this function in fact takes as input two images and project the first one on the plane of the second.
-if the second image is a painting fetched from the database, it means that the first image is rectified; if instead the second image is a painting coming from a frame/screenshot, it means that we want to distort an image in order to match the perspective of that painting.
+This function in fact takes as input two images and project the first one on the plane of the second.
+If the second image is a painting fetched from the database, it means that the first image is rectified; if instead the second image is a painting coming from a frame/screenshot, it means that we want to distort an image in order to match the perspective of that painting.
 
@@
 \centerline{\includegraphics[width=0.8\columnwidth]{../Labeling_precision_metrics/Precision_Labeling.png}}
-\caption{labeling}
+\caption{Labeling}
 \label{fig_labeling}
 \end{figure}
+\bigskip
 
 \begin{table}[htbp]
-\caption{Metrics Table}
+\caption{Performances}
 \begin{center}
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|c|}
 \hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+\textbf{} & \textbf{\textit{Paintings}} \\
 \hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
+TP& 161\\
 \hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+FP& 20\\
+\hline
+FN& 29\\
+\hline
+Average IoU& 0.860\\
+\hline
+Average Precision& 0.909\\
+\hline
+Average Recall& 0.906\\
+\hline
+Average F-Measure& 0.904\\
+\hline
 \end{tabular}
@@
 when this assumption doesn’t occur, for example in the case of a wider shot comprising hallway too, otsu doesn’t manage to correctly differentiate paintings from the rest, which leads to worse performances.
-
-\subsection{tested methods history}
+\subsection*{Tested methods history}
 At the beginning the idea was to use Canny, preceded by an initial noise removal obtained by bilateral filter, in order to find the edges on which to apply findContours opencv function.
@@
 We therefore opted for a solution based on the thresholding of the RGB image, which as already explained above is followed by a refinement carried out at the hsv level.
-A method based only on hsv images was also tested, which revealed to be very performing in certain situations (in each frame there is a clear distinction between picture and background) but less stable than the previously exposed method.
+A method based only on hsv images was also tested, which revealed to be very performing in certain situations (in each frame there is a clear distinction between picture and background) but less stable than the previously exposed method.\\
 It was then necessary to face the fact that each method, being based solely on image processing techniques, produced many false positives.
@@
 
-\section{References}
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
+\section*{}
+\section*{}
+\section*{}
 \begin{thebibliography}{00}

### 2020-06-30 PerformanceMeasures/calculator.py
table update

@@ -19,3 +19,6 @@ print('recall --> ', np.mean(recall))
 f_measure = [0.9743589743589743, 0.9166666666666667, 0.927536231884058, 1.0, 0.7058823529411764,
              0.9014084507042254]
 print('f-measure --> ', np.mean(f_measure))
+
+b = 20 + 39 + 37 + 9 + 66 + 39
+print(b)

### 2020-06-30 Paper_Presentation/paper/paper.tex
table update
completed svm evaluation and added some images to the paper

@@
 \usepackage{xcolor}
+\usepackage{csvsimple}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 First of all, each frame is converted into black and white and processed with a bilateral filter to remove noise while preserving at the same time the edges.\\
-After that, we apply otsu threshold  with the aim to separate the pixels into background and paintings, due to their chromatic difference.
+After that, we apply otsu threshold  with the aim to separate the pixels into background and paintings, due to their chromatic difference.\\
+To obtain a better result we improve the binary image by employing the closing operator to remove morphological noise like small holes.\\
+
+\bigskip
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{../detection_pipeline/1_otsu_threshold.png}
+  \caption{OTSU threshold.}
+  \label{fig:ROC_curve}
+\end{figure}
+
+\bigskip
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{../detection_pipeline/2_closing.png}
+  \caption{Closing.}
+  \label{fig:ROC_curve}
+\end{figure}
+
+\bigskip
 
@@
 Using the function findContours of OpenCV, we obtain the outlines of the objects in the foreground, among which there will also be the paintings that we are looking for.\\
+\bigskip
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{../detection_pipeline/3_contours.png}
+  \caption{Contours.}
+  \label{fig:ROC_curve}
+\end{figure}
+
+\bigskip
 We then create the bounding box containing this contours and to eliminate the rectangles identified inside the paintings, we keep only the external ones and eliminate those contained within others.\\
 Among the remaining bounding boxes, those that are not judged as paintings by an SVM model, will get discarded.
+
+\bigskip
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{../detection_pipeline/4_bb.png}
+  \caption{Bounding Boxes.}
+  \label{fig:ROC_curve}
+\end{figure}
+
+\bigskip
 
@@
 \hline
-TP& 161\\
+TP& 161/210\\
 \hline
-FP& 20\\
+FP& 20/210\\
 \hline
-FN& 29\\
+FN& 29/210\\
 \hline
@@
 \end{table}
+
+\subsection{SVM evaluation}
+The first approach, in order to test our's model's ability to predict new data and to flag problems like overfitting or selection bias, is a 10-fold cross-validation performed on the training set.
+The average of the values computed in the loop resulted in an accuracy of 88.85%.\\
+After this first check, we create a test set composed of 304 instances and calculated other score measurements on it.\\
+\begin{itemize}
+   \item  Accuracy = 0.862
+\end{itemize}
+\begin{itemize}
+   \item  Recall = 0.798
+\end{itemize}
+\begin{itemize}
+   \item  F1 = 0.825
+\end{itemize}
+\bigskip
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{../svm_curves/confusion_matrix.png}
+  \caption{Cofusion Matrix.}
+  \label{fig:Cofusion Matrix}
+\end{figure}
+
+\bigskip
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{../svm_curves/ROC_curve.png}
+  \caption{ROC.}
+  \label{fig:ROC_curve}
+\end{figure}
+
+\bigskip
+\bigskip
+\bigskip
 

### 2020-06-30 Paper_Presentation/paper/paper.tex
little changes

@@
 Each frame is processed with image processing techniques in order to localize paintings, rectify distortions, and fetch from the database the corresponding work of art.\\
-At the same time, an artificial neural network (YoloV3) detects people, which are localized inside a room of the museum.
+At the same time, an artificial neural network (YoloV3) detects people, which are localized inside a room of the museum.\\
 
@@
 ORB\cite{b5} is a feature detection algorithm like SIFT while being almost two orders of magnitude faster.
-YoloV3 \cite{b5}  is a famous neural network for fast object detection, will be used in this paper for people detection
+YoloV3 \cite{b5}  is a famous neural network for fast object detection that will be used in this paper for people detection.\\
 
@@
 To cope with this problem, the brightness component is increased for each previously found bounding box.\\
-Afterward, by transforming its format from BGR to HSV and then applying the otsu threshold again, we are able to obtain a more precise distinction between painting and frame/background, which will then be used during the retrieval and rectification steps.
+Afterward, by transforming its format from BGR to HSV and then applying the otsu threshold again, we are able to obtain a more precise distinction between painting and frame/background, which will then be used during the retrieval and rectification steps.\\
 
@@
 A ranking with the 5 best matches found is then created and saved to a CSV file to show the results.\\
-To understand if the painting is actually recognized among those in the DB, the average of the key points matched among the best 5 ranked is calculated and, if the first one differs from it for more than significant value, it is considered as correct and shown on the interface.
+To understand if the painting is actually recognized among those in the DB, the average of the key points matched among the best 5 ranked is calculated and, if the first one differs from it for more than significant value, it is considered as correct and shown on the interface.\\
 
@@
 
-\subsection{alignImages}
+\subsection{Images alignment}
 Not all the paintings inside the museum have a rectangular shape.
@@
 to avoid mismatches, the RANSAC algorithm is exploited.\\
-To obtain a better result also the inverse warping algorithm is utilized.
+To obtain a better result also the inverse warping algorithm is utilized.\\
 
@@
 With this method we assume that all the painting detected and the persons are in the same room.
-Moreover the localization will work only if the painting matched is considered safe that means the painting need to have a good level of matches, otherwise localization is not active.
+Moreover the localization will work only if the painting matched is considered safe that means the painting need to have a good level of matches, otherwise localization is not active.\\
 
@@
 This function in fact takes as input two images and project the first one on the plane of the second.
-If the second image is a painting fetched from the database, it means that the first image is rectified; if instead the second image is a painting coming from a frame/screenshot, it means that we want to distort an image in order to match the perspective of that painting.
+If the second image is a painting fetched from the database, it means that the first image is rectified; if instead the second image is a painting coming from a frame/screenshot, it means that we want to distort an image in order to match the perspective of that painting.\\
 
@@
 To calculate the precision of the presented method we took almost 10 random frame for 6 different videos and labeled all the paintings by hand using a tool for labeling (normally used for yolo labels).
-Then with a custom code we calculated precision recall… comparing hand made labels with automatically generated ones.
+Then with a custom code we calculated some metrics comparing hand made labels with automatically generated ones.
 
@@
 
-\section*{}
-\section*{}
-\section*{}
 \begin{thebibliography}{00}

### 2020-06-30 ReplacingPaintings3dModel_main.py

@@ -82,22 +82,26 @@ def main_3d(img):
                 # cv2.imshow('mask_pre', cv2.resize((mask < 1).astype(np.uint8) * 255, (700, 500)))
                 try:
                     mask = mask[y:y + h, x:x + w]
+                    sub_orig = sub_image.copy()
                     sub_image[mask] = aligned[mask]
                 except:
                     pass
+                sub_image[sub_image == (0,0,0)] = sub_orig[sub_image == (0,0,0)]
                 cv2.imshow('new', sub_image)
                 cv2.waitKey()
+                cv2.imwrite('Paper_Presentation/3DModel/replacedNew_03.png', sub_image)
+                cv2.imwrite('Paper_Presentation/3DModel/replacedOrig_03.png', sub_orig)
                 cv2.destroyAllWindows()
     cv2.destroyAllWindows()
-    cv2.imshow('before', cv2.resize(img, (800, 650)))
-    img[img == (0,0,0)] = orig[img == (0,0,0)]
-    img = cv2.resize(img, (1200, 1000))
-    cv2.imshow('after', cv2.resize(img, (800, 650)))
-    cv2.waitKey()
-    cv2.imwrite('Paper_Presentation/3DModel/replaced_10.png', img)
+    # cv2.imshow('before', cv2.resize(img, (800, 650)))
+    # img[img == (0,0,0)] = orig[img == (0,0,0)]
+    # img = cv2.resize(img, (1200, 1000))
+    # cv2.imshow('after', cv2.resize(img, (800, 650)))
+    # cv2.waitKey()
+    cv2.imwrite('Paper_Presentation/3DModel/replaced_03.png', img)
     return img
 
 
 if __name__ == '__main__':
-    img = cv2.imread('screenshots_3d_model/screenshot_10.jpg', cv2.IMREAD_COLOR)
+    img = cv2.imread('screenshots_3d_model/screenshot_03.png', cv2.IMREAD_COLOR)
     main_3d(img)

### 2020-06-30 ReplacingPaintings3dModel_main.py
3d model figures added

@@ -89,8 +89,8 @@ def main_3d(img):
                 sub_image[sub_image == (0,0,0)] = sub_orig[sub_image == (0,0,0)]
                 cv2.imshow('new', sub_image)
                 cv2.waitKey()
-                cv2.imwrite('Paper_Presentation/3DModel/replacedNew_03.png', sub_image)
-                cv2.imwrite('Paper_Presentation/3DModel/replacedOrig_03.png', sub_orig)
+                cv2.imwrite('Paper_Presentation/3DModel/replacedNew_07.png', sub_image)
+                cv2.imwrite('Paper_Presentation/3DModel/replacedOrig_07.png', sub_orig)
                 cv2.destroyAllWindows()
     cv2.destroyAllWindows()
     # cv2.imshow('before', cv2.resize(img, (800, 650)))
@@ -98,10 +98,10 @@ def main_3d(img):
     # img = cv2.resize(img, (1200, 1000))
     # cv2.imshow('after', cv2.resize(img, (800, 650)))
     # cv2.waitKey()
-    cv2.imwrite('Paper_Presentation/3DModel/replaced_03.png', img)
+    cv2.imwrite('Paper_Presentation/3DModel/replaced_07.png', img)
     return img
 
 
 if __name__ == '__main__':
-    img = cv2.imread('screenshots_3d_model/screenshot_03.png', cv2.IMREAD_COLOR)
+    img = cv2.imread('screenshots_3d_model/screenshot_07.jpg', cv2.IMREAD_COLOR)
     main_3d(img)

### 2020-06-30 Paper_Presentation/paper/paper.tex
3d model figures added
hyperref

@@
 \usepackage{csvsimple}
+\usepackage{hyperref}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-A little problem has arisen due to the high number of paintings representing persons, in fact the network detect them also inside the paintings, to prevent these false positive we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting.
+A little problem has arisen due to the high number of paintings representing persons as show in figure \ref{fig_People_detection_error}, in fact the network detect them also inside the paintings, to prevent these false positive we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting.
 
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.8\columnwidth]{../screenshots_3d_model/screenshot_01.jpg}}
-\caption{3dmodel}
+\centerline{\includegraphics[width=0.8\columnwidth]{../3DModel/collage_06.jpg}}
+\caption{Original image vs Superimposed image}
 \label{fig_3d_model}
-\end{figure}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.8\columnwidth]{../screenshots_3d_model/screenshot_03.png}}
-\caption{3d model 2}
-\label{fig_3d_model_2}
 \end{figure}

### 2020-06-30 ReplacingPaintings3dModel_main.py
cleaning

@@ -29,9 +29,6 @@ def main_3d(img):
     for c in cnts1:
         if cv2.contourArea(c) < 100:
             continue
-        # approximate the contour
-        peri = cv2.arcLength(c, True)
-        approx = cv2.approxPolyDP(c, 0.02 * peri, True)
         (x0, y0, w0, h0) = cv2.boundingRect(c)
         # if len(approx) == 4:
         if check_roi(img[y0:y0 + h0, x0:x0 + w0]):
@@ -39,9 +36,6 @@ def main_3d(img):
     for c in cnts2:
         if cv2.contourArea(c) < 100:
             continue
-        # approximate the contour
-        peri = cv2.arcLength(c, True)
-        approx = cv2.approxPolyDP(c, 0.02 * peri, True)
         (x0, y0, w0, h0) = cv2.boundingRect(c)
         # if len(approx) == 4:
         if check_roi(img[y0:y0 + h0, x0:x0 + w0]):
@@ -84,20 +78,14 @@ def main_3d(img):
                     mask = mask[y:y + h, x:x + w]
                     sub_orig = sub_image.copy()
                     sub_image[mask] = aligned[mask]
+                    sub_image[sub_image == (0,0,0)] = sub_orig[sub_image == (0,0,0)]
+                    cv2.imshow('new', sub_image)
+                    cv2.waitKey()
+                    cv2.imwrite('Paper_Presentation/3DModel/replacedNew_07.png', sub_image)
+                    cv2.imwrite('Paper_Presentation/3DModel/replacedOrig_07.png', sub_orig)
                 except:
                     pass
-                sub_image[sub_image == (0,0,0)] = sub_orig[sub_image == (0,0,0)]
-                cv2.imshow('new', sub_image)
-                cv2.waitKey()
-                cv2.imwrite('Paper_Presentation/3DModel/replacedNew_07.png', sub_image)
-                cv2.imwrite('Paper_Presentation/3DModel/replacedOrig_07.png', sub_orig)
                 cv2.destroyAllWindows()
-    cv2.destroyAllWindows()
-    # cv2.imshow('before', cv2.resize(img, (800, 650)))
-    # img[img == (0,0,0)] = orig[img == (0,0,0)]
-    # img = cv2.resize(img, (1200, 1000))
-    # cv2.imshow('after', cv2.resize(img, (800, 650)))
-    # cv2.waitKey()
     cv2.imwrite('Paper_Presentation/3DModel/replaced_07.png', img)
     return img
 

### 2020-06-30 main.py

@@ -99,7 +99,6 @@ class AnalyzerGUI:
         self.museum_map_label.grid(row=2, column=0)
 
         # --------- Rectified paintings frame and container ---------
-        # ToDo: print rectified images on GUI
         self.rect_paint_frame = LabelFrame(self.master, text="Rectified Paintings")
         self.rect_paint_frame.grid(row=0, column=1, rowspan=3)
         self.rectified_array = [Label(self.rect_paint_frame, image=""),Label(self.rect_paint_frame, image=""),Label(self.rect_paint_frame, image=""),Label(self.rect_paint_frame, image="")]
@@ -114,7 +113,6 @@ class AnalyzerGUI:
             self.rectified_array[i].grid(row=i, column=0)
 
         # --------- Matched paintings frame and container ---------
-        # ToDo: print matched images on GUI
         self.match_paint_frame = LabelFrame(self.master, text="Matched Paintings")
         self.match_paint_frame.grid(row=0, column=2, rowspan=3)
         self.matched_array = [Label(self.match_paint_frame, image=""),Label(self.match_paint_frame, image=""),Label(self.match_paint_frame, image=""),Label(self.match_paint_frame, image="")]
@@ -181,7 +179,6 @@ class AnalyzerGUI:
             height = cap.get(cv2.CAP_PROP_FRAME_HEIGHT)
             height_scale = height / float(self.out_video_dim[1])
             width_scale = width / float(self.out_video_dim[0])
-            scale_percent = 1
             if width_scale > height_scale:
                 scale_percent = width_scale
             else:
@@ -208,11 +205,6 @@ class AnalyzerGUI:
                 # Print actual video frame on the gui
                 self.print_on_GUI(frameWithBB, self.video_label, self.out_video_dim)
 
-                # just some testing to create the db for svm
-                # if frame_counter % 100 == 0:
-                #     for box in bounding_boxes:
-                #         label_hist(frame[box[1]:box[1] + box[3], box[0]:box[0] + box[2]])
-
                 # Print Map with actual room
                 found = 0
                 if len(paintings_matched) != 0:
@@ -230,7 +222,6 @@ class AnalyzerGUI:
                 for j in range(self.max_num_matched_paint):
                     if j < len(paintings_matched) and paintings_matched[j]:
                         height, width, channels = paintings_matched[j][0]['im'].shape
-                        scale_rect = 1
                         height_scale = height / float(self.matched_dim[1])
                         width_scale = width / float(self.matched_dim[0])
                         if width_scale > height_scale:
[…]

### 2020-06-30 Paper_Presentation/paper/paper.tex

@@
 First of all, each frame is converted into black and white and processed with a bilateral filter to remove noise while preserving at the same time the edges.\\
-After that, we apply otsu threshold  with the aim to separate the pixels into background and paintings, due to their chromatic difference.\\
-To obtain a better result we improve the binary image by employing the closing operator to remove morphological noise like small holes.\\
+After that, we apply otsu threshold (figure \ref{fig:1_otsu_threshold}) with the aim to separate the pixels into background and paintings, due to their chromatic difference.\\
+To obtain a better result we improve the binary image by employing the closing operator (figure \ref{fig:2_closing}) to remove morphological noise like small holes.\\
 
@@
   \caption{OTSU threshold.}
-  \label{fig:ROC_curve}
+  \label{fig:1_otsu_threshold}
 \end{figure}
@@
   \caption{Closing.}
-  \label{fig:ROC_curve}
+  \label{fig:2_closing}
 \end{figure}
@@
 \subsection{Bounding Box detection}
-Using the function findContours of OpenCV, we obtain the outlines of the objects in the foreground, among which there will also be the paintings that we are looking for.\\
+Using the function findContours of OpenCV, we obtain the outlines of the objects in the foreground (figure \ref{fig:3_contours}), among which there will also be the paintings that we are looking for.\\
 \bigskip
@@
   \caption{Contours.}
-  \label{fig:ROC_curve}
+  \label{fig:3_contours}
 \end{figure}
@@
 We then create the bounding box containing this contours and to eliminate the rectangles identified inside the paintings, we keep only the external ones and eliminate those contained within others.\\
-Among the remaining bounding boxes, those that are not judged as paintings by an SVM model, will get discarded.
+Among the remaining bounding boxes, those that are not judged as paintings by an SVM model, will get discarded as shown in figure \ref{fig:4_bb}.
 
@@
   \caption{Bounding Boxes.}
-  \label{fig:ROC_curve}
+  \label{fig:4_bb}
 \end{figure}
@@
 For the retrieval of the paintings situated in the database we use an approach based on feature detection algorithms.\\ 
-After consulting a paper that performs a comparative analysis between the most well known algorithms ~\cite{b1} to get a general idea of the strengths and weaknesses of the different methods available to us, we carried out some experiments focusing on SIFT, AKAZE and ORB.\\
+After consulting a paper that performs a comparative analysis between the most well known algorithms ~\cite{b7} to get a general idea of the strengths and weaknesses of the different methods available to us, we carried out some experiments focusing on SIFT, AKAZE and ORB.\\
 The results obtained made us opt for ORB, because overall it gave us more precise results than AKAZE and, unlike SIFT, it’s free of charge, therefore usable without fees in a possible commercial application.\\
-To save time, the key points of the paintings in the database have been previously calculated and stored using the pickle module [link pickle documentation].\\
+To save time, the key points of the paintings in the database have been previously calculated and stored using the pickle module \cite{b8}.\\
 It implements binary protocols for serializing and de-serializing a Python object structure.\\
 This data is loaded only once during the launch of the program.
-The key points are computed from the bounding boxes detected by the previously described pipeline and afterward, to determine the best matches, the ratio test proposed by D.
-Lowe in the SIFT paper is performed[Reference to the sift paper].\\
+The key points are computed from the bounding boxes detected by the previously described pipeline and afterward (figure \ref{fig_Orb_matches}), to determine the best matches, the ratio test proposed by D.
+Lowe in the SIFT paper is performed \cite{b9}.\\
 This measure is obtained by comparing the distance of the closest neighbor to that of the second-closest neighbor.\\
@@
 Given the four points, we are able to estimate the homography and apply the transformation to rectify the painting.\\
-To calculate the aspect ratio for the projected rectangle we use an implementation based on this paper [] which derives the equations assuming a pinhole camera model.\\
+To calculate the aspect ratio for the projected rectangle we use an implementation based on this paper \cite{b10} which derives the equations assuming a pinhole camera model.\\
 This pipeline is applied to the paintings that don't get a match on the database.
@@
 The weights for the network are obtained from an already trained network on COCO[ reference to COCO paper], a famous dataset containing 80 different classes.\\
-In our case the only wanted class is the person one, for ease of use the network has not been modified, but from its output will be deleted all the classes with an id different from 0 that is the id of the person class.\\
+In our case the only wanted class is the person one, for ease of use the network has not been modified, but from its output will be deleted all the classes with an id different from 0 that is the id of the person class \ref{fig_People_detection} .\\
 
@@
 
-A little problem has arisen due to the high number of paintings representing persons as show in figure \ref{fig_People_detection_error}, in fact the network detect them also inside the paintings, to prevent these false positive we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting.
+A little problem has arisen due to the high number of paintings representing persons as show in figure \ref{fig_People_detection_error}, in fact the network detect them also inside the paintings, to prevent these false positive we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting \ref{fig_People_detection_error}.
 
@@
 At this point we loop over each contour and find an approximation of itself with approxPolyDP; if the approximation has a shape described by 4 vertices, we estimate keypoints with orb and fetch the corresponding image from the database.
-Once this is done, if the image fetched is judged as a good match, we align that image with respect to the screenshot’s image plane and superimpose the result on the input image.
+Once this is done, if the image fetched is judged as a good match, we align that image with respect to the screenshot’s image plane and superimpose the result on the input image as shown in figure \ref{fig_3d_model}.
 
@@
 \section{Metrics and Precision}
-To calculate the precision of the presented method we took almost 10 random frame for 6 different videos and labeled all the paintings by hand using a tool for labeling (normally used for yolo labels).
+To calculate the precision of the presented method we took almost 10 random frame for 6 different videos and labeled all the paintings by hand using a tool for labeling (normally used for yolo labels) \ref{fig_labeling}.
 Then with a custom code we calculated some metrics comparing hand made labels with automatically generated ones.
@@
 doi:10.1016/0734-189X(85)90016-7.
-\bibitem{b4} 
+\bibitem{b4} \url{https://docs.opencv.org/2.4/modules/imgproc/doc/structural_analysis_and_shape_descriptors.html#approxpolydp}
 \bibitem{b5} E.
@@
 \bibitem{b6}Redmon, Joseph and Ali Farhadi. “YOLOv3: An Incremental Improvement.” ArXiv abs/1804.02767 (2018): n. pag.
+\bibitem{b7}Tareen, Shaharyar Ahmed Khan, and Zahra Saleem.
+"A comparative analysis of sift, surf, kaze, akaze, orb, and brisk." 2018 International conference on computing, mathematics and engineering technologies (iCoMET).
+IEEE, 2018.
+\bibitem{b8} \url{https://docs.python.org/3/library/pickle.html}
+\bibitem{b9} Lowe, David G. "Distinctive image features from scale-invariant keypoints." International journal of computer vision 60.2 (2004): 91-110.
+\bibitem{b10}Zhang, Zhengyou, and Li-Wei He. "Whiteboard scanning and image enhancement." Digital Signal Processing 17.2 (2007): 414-432.
+
 \end{thebibliography}

### 2020-06-30 Paper_Presentation/paper/paper.tex
paper

@@
 YoloV3 \cite{b5}  is a famous neural network for fast object detection that will be used in this paper for people detection.\\
+A graphical user interfaces has been created to show the work and process automatically the video using tkinter \cite{b12}
 
@@
 At inference time each video frame is passed through the network that find all bounding boxes containing one of the objects in our classes list.\\
-The weights for the network are obtained from an already trained network on COCO[ reference to COCO paper], a famous dataset containing 80 different classes.\\
+The weights for the network are obtained from an already trained network on COCO \cite{b11}, a famous dataset containing 80 different classes.\\
 In our case the only wanted class is the person one, for ease of use the network has not been modified, but from its output will be deleted all the classes with an id different from 0 that is the id of the person class \ref{fig_People_detection} .\\
@@
 
+\section{GUI}
+A graphical user interface has been created using tkinter library \cite{b12} to show in real time what our program is doing.
+It’s also capable to process new video simply by typing its name into the input field.
+Two different threads run at the same time, one for the gui and the other one for our pipeline.
+After a complete analysis, a new video is created showing what the interface has displayed for the entire time of its utilization.
+
 \section{Discussions}
@@
 \bibitem{b10}Zhang, Zhengyou, and Li-Wei He. "Whiteboard scanning and image enhancement." Digital Signal Processing 17.2 (2007): 414-432.
+\bibitem{b11}Lin TY.
+et al.
+(2014) Microsoft COCO: Common Objects in Context.
+In: Fleet D., Pajdla T., Schiele B., Tuytelaars T.
+(eds) Computer Vision – ECCV 2014.
+ECCV 2014.
+Lecture Notes in Computer Science, vol 8693.
+Springer, Cham
+\bibitem{b12} \url{https://docs.python.org/3/library/tkinter.html}
 

### 2020-06-30 Paper_Presentation/paper/paper.tex
last paper?

@@
 YoloV3 \cite{b5}  is a famous neural network for fast object detection that will be used in this paper for people detection.\\
-A graphical user interfaces has been created to show the work and process automatically the video using tkinter \cite{b12}
+A graphical user interfaces has been created to show the work and process automatically the video using tkinter \cite{b12}\\
 
@@
 
-\bigskip
-
 \subsection{SVM}
@@
 The results obtained made us opt for ORB, because overall it gave us more precise results than AKAZE and, unlike SIFT, it’s free of charge, therefore usable without fees in a possible commercial application.\\
-To save time, the key points of the paintings in the database have been previously calculated and stored using the pickle module \cite{b8}.\\
-It implements binary protocols for serializing and de-serializing a Python object structure.\\
+To save time, the key points of the paintings in the database have been previously calculated and stored using the pickle module \cite{b8}.
+It implements binary protocols for serializing and de-serializing a Python object structure.
 This data is loaded only once during the launch of the program.
-The key points are computed from the bounding boxes detected by the previously described pipeline and afterward (figure \ref{fig_Orb_matches}), to determine the best matches, the ratio test proposed by D.
+The key points are computed from the bounding boxes detected by the previously described pipeline and afterward (figure ~\ref{fig_Orb_matches}), to determine the best matches, the ratio test proposed by D.
 Lowe in the SIFT paper is performed \cite{b9}.\\
@@
 For false matches, there will likely be a number of other false matches within similar distances due to the high dimensionality of the feature space.\\
-In our implementation we reject all matches in which the distance ratio is greater than 0.75.\\
+In our implementation we reject all matches in which the distance ratio is greater than 0.75.
 This allows us to keep the number of correctly retrieved paintings still high but at the same time to decrease the number of false positive.
-A ranking with the 5 best matches found is then created and saved to a CSV file to show the results.\\
+A ranking with the 5 best matches found is then created and saved to a CSV file to show the results.
 To understand if the painting is actually recognized among those in the DB, the average of the key points matched among the best 5 ranked is calculated and, if the first one differs from it for more than significant value, it is considered as correct and shown on the interface.\\
@@
 
-A little problem has arisen due to the high number of paintings representing persons as show in figure \ref{fig_People_detection_error}, in fact the network detect them also inside the paintings, to prevent these false positive we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting \ref{fig_People_detection_error}.
+A little problem has arisen due to the high number of paintings representing persons as show in figure \ref{fig_People_detection_error}, in fact the network detect them also inside the paintings, to prevent these false positive we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting, the result is shown in figure\ref{fig_People_detection_error_fixed}.\\
 
@@
 \end{figure}
+
+\bigskip
 
@@
 \end{figure}
-\bigskip
 
@@
 
+\bigskip
+
 \section{Discussions}
@@
 many correctly identified paintings were in fact discarded because they were not present in the database.
-The solution adopted was to train an svm with the goal to classify what is a painting and what is not.
+The solution adopted was to train an svm with the goal to classify what is a painting and what is not.\\
 

### 2020-06-30 Paper_Presentation/paper/paper.tex
Paper grammar fix

@@
 \section{Related Works}
-To remove camera noise but maintains the contours a  Bilateral filter\cite{b1} is used.
+To remove camera noise but maintain the contours a Bilateral filter\cite{b1} is used.
 OTSU\cite{b2} is an automatic thresholding method widely used when the numbers of pixels in each class are close to each other.
-Opencv Find Counturs\cite{b3} function is been used to find counturs in a previouslly modified frame in order to detect painting
-The functions approxPolyDP\cite{b4} approximate a curve or a polygon with another curve/polygon with less vertices so that the distance between them is less or equal to the specified precision.
-It uses the Douglas-Peucker algorithm
+OpenCV Find Counturs\cite{b3} function is been used to find counturs in a previouslly modified frame in order to detect each painting.
+The function approxPolyDP\cite{b4} approximates a curve or a polygon with another curve/polygon with less vertices so that the distance between them is less or equal to the specified precision.
+It uses the Douglas-Peucker algorithm.
 ORB\cite{b5} is a feature detection algorithm like SIFT while being almost two orders of magnitude faster.
 YoloV3 \cite{b5} is a famous neural network for fast object detection that will be used in this paper for people detection.\\
-A graphical user interfaces has been created to show the work and process automatically the video using tkinter \cite{b12}\\
+A graphical user interface has been created to show the work and process automatically videos using tkinter \cite{b12}.\\
 
@@
 First of all, each frame is converted into black and white and processed with a bilateral filter to remove noise while preserving at the same time the edges.\\
-After that, we apply otsu threshold (figure \ref{fig:1_otsu_threshold}) with the aim to separate the pixels into background and paintings, due to their chromatic difference.\\
+After that, we apply otsu threshold (figure \ref{fig:1_otsu_threshold}) with the aim to segment pixels as background and paintings, thanks to their chromatic difference.\\
 To obtain a better result we improve the binary image by employing the closing operator (figure \ref{fig:2_closing}) to remove morphological noise like small holes.\\
@@
 \subsection{Bounding Box detection}
-Using the function findContours of OpenCV, we obtain the outlines of the objects in the foreground (figure \ref{fig:3_contours}), among which there will also be the paintings that we are looking for.\\
+Using the function findContours of OpenCV we obtain the outlines of the objects in the foreground (figure \ref{fig:3_contours}), among which there will be also the paintings that we are looking for.\\
 \bigskip
@@
 \bigskip
-We then create the bounding box containing this contours and to eliminate the rectangles identified inside the paintings, we keep only the external ones and eliminate those contained within others.\\
+Then we create the bounding boxes containing this contours, keeping only the external ones and eliminate those contained within others (in order to eliminate the rectangles identified inside the paintings).\\
 Among the remaining bounding boxes, those that are not judged as paintings by an SVM model, will get discarded as shown in figure \ref{fig:4_bb}.
@@
 \subsection{SVM}
-To classify the ROI proposed by the previous pipeline, an SVM model is been trained.\\
-The algorithm takes as input the concatenation of the three histograms, one for each color plane.\\
-The training dataset is composed of 1025 instances taken from bounding boxes derivate from the videos inside the museum and manually labeled.
-409 of the samples are labeled as holding a painting and 604 as inaccurate bounding box.\\
+To classify the ROIs proposed by the previous pipeline, an SVM model is been trained.\\
+The algorithm takes as input the concatenation of three histograms, one for each color plane.\\
+The training dataset is composed of 1025 instances taken from bounding boxes coming from the videos taken inside the museum and manually labeled.
+409 of the samples are labeled as holding a painting and 604 as inaccurate bounding boxes.\\
 A radial basis function kernel is been exploited for the classification.
@@
 To obtain a better segmentation within each bounding box we apply a further refinement of the images.\\
-Observing the low light in the videos that were provided to us, the paintings\\
-are significantly darker compared to their frame and do not correspond to the brightness of the paintings in the database.
+Observing the low light in the videos that were provided to us, the paintings are significantly darker compared to their frame and do not correspond to the brightness of the paintings in the database.
 This leads to poor precision in the retrieval step.
-To cope with this problem, the brightness component is increased for each previously found bounding box.\\
-Afterward, by transforming its format from BGR to HSV and then applying the otsu threshold again, we are able to obtain a more precise distinction between painting and frame/background, which will then be used during the retrieval and rectification steps.\\
+To cope with this problem, the brightness component of each bounding box is increased.\\
+Afterward, by transforming the format from BGR to HSV and then applying the otsu threshold again, we are able to obtain a more precise distinction between painting and background, which will be used during the retrieval and rectification steps.\\
 
 \section{Painting Retrieval}
-For the retrieval of the paintings situated in the database we use an approach based on feature detection algorithms.\\ 
+The retrieval of the paintings situated in the database is accomplished using an approach based on feature detection algorithms.\\ 
 After consulting a paper that performs a comparative analysis between the most well known algorithms ~\cite{b7} to get a general idea of the strengths and weaknesses of the different methods available to us, we carried out some experiments focusing on SIFT, AKAZE and ORB.\\
-The results obtained made us opt for ORB, because overall it gave us more precise results than AKAZE and, unlike SIFT, it’s free of charge, therefore usable without fees in a possible commercial application.\\
+The results obtained led us to ORB, because it gave us more precise overall results than AKAZE and, unlike SIFT, it’s free of charge, therefore usable without fees in a possible commercial application.\\
 To save time, the key points of the paintings in the database have been previously calculated and stored using the pickle module \cite{b8}.
 It implements binary protocols for serializing and de-serializing a Python object structure.
-This data is loaded only once during the launch of the program.
+This data is loaded only once during the launch of the program (singleton pattern has been used).
 The key points are computed from the bounding boxes detected by the previously described pipeline and afterward (figure ~\ref{fig_Orb_matches}), to determine the best matches, the ratio test proposed by D.
 Lowe in the SIFT paper is performed \cite{b9}.\\
-This measure is obtained by comparing the distance of the closest neighbor to that of the second-closest neighbor.\\
-This measure performs well because correct matches need to have the closest neighbor significantly closer than the closest incorrect match to achieve reliable matching.\\
+This measure is obtained by comparing the distance of the closest neighbor to the one of the second-closest neighbor.\\
+It performs well because correct matches need to have the closest neighbor significantly closer than the closest incorrect match to achieve reliable matching.\\
 
@@
 
-For false matches, there will likely be a number of other false matches within similar distances due to the high dimensionality of the feature space.\\
+Likely, there will be a number of other false positives within similar distances due to the high dimensionality of the feature space.\\
 In our implementation we reject all matches in which the distance ratio is greater than 0.75.
-This allows us to keep the number of correctly retrieved paintings still high but at the same time to decrease the number of false positive.
+This allows us to keep the number of correctly retrieved paintings still high but at the same time to decrease the number of false positives.
 A ranking with the 5 best matches found is then created and saved to a CSV file to show the results.
-To understand if the painting is actually recognized among those in the DB, the average of the key points matched among the best 5 ranked is calculated and, if the first one differs from it for more than significant value, it is considered as correct and shown on the interface.\\
+To understand if the painting is actually recognized among those in the DB, the average of the key points matched among the best 5 is calculated; if the first one differs from it for more than a certain value, it is considered correct and shown on the interface.\\
 
@@
 \subsection{Four points transform}
-On the contour found with the techniques described in \textbf{Precision boosting and paintings segmentation} is applied the function approxPolyDP from OpenCV to approximate it to a polygonal curve.\\
+Over the contour found with the techniques described in \textbf{Precision boosting and paintings segmentation} is applied the function approxPolyDP from OpenCV to approximate it to a polygonal curve.\\
 If the shape returned has four vertices we can assume that the process has found a rectangular painting.\\
@@
 The approach that is used in this case is based on the common keypoints found between the distorted image and the corresponding match in the database.\\
-Through ORB feature matching algorithm the key points are computed from each bounding boxes detected by the previous pipeline and subsequently, to determine the best matches between it and the images of the database, the ratio test is used.\\
-From them we calculate the homography matrix and
+Through ORB feature matching algorithm the key points are computed from each bounding box detected by the previous pipeline.
+Subsequently the ratio test is used to determine the best matches between it and the images of the database.\\
+From them we calculate the homography matrix and,
 to avoid mismatches, the RANSAC algorithm is exploited.\\
-To obtain a better result also the inverse warping algorithm is utilized.\\
+To obtain a better result the inverse warping algorithm is utilized too.\\
 
@@
 A neural network (YoloV3) is used for people detection.\\
-At inference time each video frame is passed through the network that find all bounding boxes containing one of the objects in our classes list.\\
+At inference time each video frame is passed through the network that finds out all bounding boxes containing one of the objects in our classes list.\\
 The weights for the network are obtained from an already trained network on COCO \cite{b11}, a famous dataset containing 80 different classes.\\
-In our case the only wanted class is the person one, for ease of use the network has not been modified, but from its output will be deleted all the classes with an id different from 0 that is the id of the person class \ref{fig_People_detection} .\\
+In our case the only wanted class is the person one, for ease of use the network has not been modified, but from its output will be deleted all the classes with an id different from 0 (person class).\\
 
@@
 
-A little problem has arisen due to the high number of paintings representing persons as show in figure \ref{fig_People_detection_error}, in fact the network detect them also inside the paintings, to prevent these false positive we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting, the result is shown in figure\ref{fig_People_detection_error_fixed}.\\
+A little problem has arisen due to the high number of paintings representing people as show in figure \ref{fig_People_detection_error}, in fact the network detect them also inside the paintings.
+To prevent these false positives we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting.
+The result is shown in figure \ref{fig_People_detection_error_fixed}.\\
 
@@
 \section{People Localization}
-Starting from a previously detected and retrieved painting from the database, we search the corresponding room in csv file, then a little red dot is printed on the museum image map.
-With this method we assume that all the painting detected and the persons are in the same room.
-Moreover the localization will work only if the painting matched is considered safe that means the painting need to have a good level of matches, otherwise localization is not active.\\
+Starting from a previously detected and retrieved painting, we look for the corresponding room in the csv file.
+Then a little red dot is printed on the museum image map.
+With this method we assume that all the paintings detected and the people are in the same room.
+Moreover the localization will work only if the painting matched is considered safe, that means the painting need to have a good level of matches. Otherwise localization is not active.\\
 
@@
 The pipeline followed to accomplish this task is similar to the one explained before with a little difference.
-It starts directly with the hsv version of the image taken as input (a screenshot from the 3d model); then we apply Otsu threshold, followed by noise removal thanks to opening or closing process, keeping the one that maximizes the number of contours found.
-At this point we loop over each contour and find an approximation of itself with approxPolyDP; if the approximation has a shape described by 4 vertices, we estimate keypoints with orb and fetch the corresponding image from the database.
-Once this is done, if the image fetched is judged as a good match, we align that image with respect to the screenshot’s image plane and superimpose the result on the input image as shown in figure \ref{fig_3d_model}.
+It starts directly with the HSV version of the image taken as input (a screenshot from the 3d model); then we apply Otsu threshold, followed by noise removal thanks to opening or closing process, keeping the one that maximizes the number of contours found.
+At this point we loop over each contour and find an approximation with approxPolyDP; if the approximation has a shape described by 4 vertices, we estimate keypoints with ORB and fetch the corresponding image from the database.
+After that, if the image fetched is judged as a good match, we align that image with respect to the screenshot’s image plane and superimpose the result on the input image as shown in figure \ref{fig_3d_model}.
 
@@
 
-What is worth to mention is that the alignment function that we use in this process is the same of the main pipeline of painting rectification.
-This function in fact takes as input two images and project the first one on the plane of the second.
+What is worth to mention is that the alignment function that we use in this process is the same used in the main pipeline of painting rectification.
+This function in fact takes as input two images and project the first one on the plane of the second one.
 If the second image is a painting fetched from the database, it means that the first image is rectified; if instead the second image is a painting coming from a frame/screenshot, it means that we want to distort an image in order to match the perspective of that painting.\\
@@
 \section{Metrics and Precision}
-To calculate the precision of the presented method we took almost 10 random frame for 6 different videos and labeled all the paintings by hand using a tool for labeling (normally used for yolo labels) \ref{fig_labeling}.
+To calculate the precision of the presented method we took almost 10 random frame for 6 different videos and labeled all the paintings by hand using a tool for labeling (normally used for yolo labels).
 Then with a custom code we calculated some metrics comparing hand made labels with automatically generated ones.
@@
 \subsection{SVM evaluation}
-The first approach, in order to test our's model's ability to predict new data and to flag problems like overfitting or selection bias, is a 10-fold cross-validation performed on the training set.
-The average of the values computed in the loop resulted in an accuracy of 88.85%.\\
+The first approach, in order to test our model's ability to predict new data and to flag problems like overfitting or selection bias, is a 10-fold cross-validation performed on the training set.
+The average of the values computed in the loop resulted in an accuracy of 88.85\%.\\
 After this first check, we create a test set composed of 304 instances and calculated other score measurements on it.\\
@@
 Our approach is based on the assumption that input videos contain a relevant chromatic difference between paintings and background.
-when this assumption doesn’t occur, for example in the case of a wider shot comprising hallway too, otsu doesn’t manage to correctly differentiate paintings from the rest, which leads to worse performances.
+When this assumption doesn’t occur, for example in the case of a wider shot comprising hallway too, Otsu doesn’t manage to differentiate paintings from the rest correctly, which leads to worse performances.
 \subsection*{Tested methods history}
-At the beginning the idea was to use Canny, preceded by an initial noise removal obtained by bilateral filter, in order to find the edges on which to apply findContours opencv function.
-The results were not entirely satisfactory as the outlines often produced by canny did not accurately identify the picture.
-We therefore opted for a solution based on the thresholding of the RGB image, which as already explained above is followed by a refinement carried out at the hsv level.
-A method based only on hsv images was also tested, which revealed to be very performing in certain situations (in each frame there is a clear distinction between picture and background) but less stable than the previously exposed method.\\
-It was then necessary to face the fact that each method, being based solely on image processing techniques, produced many false positives.
+At the beginning the idea was to use Canny, preceded by an initial noise removal obtained thanks to a bilateral filter, in order to find the edges on which to apply findContours OpenCV function.
+The results were not entirely satisfactory as the outlines often produced by Canny did not accurately identify the picture.
+We therefore opted for a solution based on the thresholding of the RGB image, which as already explained above is followed by a refinement carried out at the HSV level.
+A method based only on HSV images was also tested, which revealed to be very performing in certain situations (in each frame there is a clear distinction between picture and background) but less stable than the previously exposed method.\\
+Then it was necessary to face the fact that each method, being based solely on image processing techniques, produced many false positives.
 The simplest way, according to which only bounding boxes containing a painting that had been matched on the database should have been shown, was discarded due to the limited database.
-many correctly identified paintings were in fact discarded because they were not present in the database.
+Many correctly identified paintings were in fact discarded because they were not present in the database.
 The solution adopted was to train an svm with the goal to classify what is a painting and what is not.\\

### 2020-07-01 PerformanceMeasures/calculator.py
update delle 2:14

@@ -1,24 +1,30 @@
 import numpy as np
 
 
-iou = [0.8147501200102073, 0.8231272445670029, 0.8822576065854896, 0.9415498728059168, 0.9135807202871309,
+iou = [0.8147501200102073, 0.823127244567003, 0.8822576065854896, 0.9415498728059168, 0.9135807202871309,
        0.7864487585693898]
 
 print(np.mean(iou))
 
-a = 32 + 36 + 9 + 32 + 33 + 19
-print(a)
+tp = 32 + 36 + 9 + 32 + 33 + 19
+print('tp: ', tp)
 
-precision = [0.8888888888888888, 0.8372093023255814, 1.0, 0.8888888888888888, 0.8918918918918919,
-             0.95]
+fp = 6 + 4 + 7 + 7 + 7
+print('fp: ', fp)
+
+fn = 8 + 26 + 5 + 3 + 2
+print('fn: ', fn)
+
+precision = [0.76, 0.8918918918918919, 0.8205128205128205, 1.0, 0.8372093023255814,
+             0.8205128205128205]
 print('precision --> ', np.mean(precision))
 
-recall = [0.9142857142857143, 0.6101694915254238, 1.0, 0.9696969696969697, 0.9428571428571428, 1.0]
+recall = [0.8, 0.5806451612903226, 1.0, 0.8648648648648649, 0.9166666666666666, 0.9047619047619048]
 print('recall --> ', np.mean(recall))
 
-f_measure = [0.9743589743589743, 0.9166666666666667, 0.927536231884058, 1.0, 0.7058823529411764,
-             0.9014084507042254]
+f_measure = [0.8260869565217391, 0.9041095890410958, 0.8421052631578947, 1.0, 0.6857142857142857,
+             0.810126582278481]
 print('f-measure --> ', np.mean(f_measure))
 
-b = 20 + 39 + 37 + 9 + 66 + 39
-print(b)
+b = 27 + 40 + 44 + 9 + 69 + 47
+print('tot bb: ', b)

### 2020-07-01 PerformanceMeasures/performanceMain.py

@@ -29,7 +29,7 @@ def IoU(bb1, bb2, frameW, frameH):
 
 frameW = 1280
 frameH = 720
-files = glob.glob("vid01/*.txt")
+files = glob.glob("vid12/*.txt")
 iou_list = []
 tp = 0
 fp = 0

### 2020-07-01 Paper_Presentation/paper/paper.tex
update delle 2:14
fine

@@
 \end{figure}
-\bigskip
 
-Likely, there will be a number of other false positives within similar distances due to the high dimensionality of the feature space.\\
+Likely, there will be a number of other false positives within similar distances due to the high dimensionality of the feature space.
 In our implementation we reject all matches in which the distance ratio is greater than 0.75.
@@
 To calculate the aspect ratio for the projected rectangle we use an implementation based on this paper \cite{b10} which derives the equations assuming a pinhole camera model.\\
-This pipeline is applied to the paintings that don't get a match on the database.
+Another method based on the work done at PyImageSearch\cite{b13} is used in order to rectificate the painting given the four points of the contour.
 
@@
 \hline
-TP& 161/210\\
+TP& 161/236\\
 \hline
-FP& 20/210\\
+FP& 31/236\\
 \hline
-FN& 29/210\\
+FN& 44/236\\
 \hline
@@
 \hline
-Average Precision& 0.909\\
+Average Precision& 0.855\\
 \hline
-Average Recall& 0.906\\
+Average Recall& 0.844\\
 \hline
-Average F-Measure& 0.904\\
+Average F-Measure& 0.845\\
 \hline
@@
 \bibitem{b12} \url{https://docs.python.org/3/library/tkinter.html}
+\bibitem{b13} \url{https://www.pyimagesearch.com/2014/08/25/4-point-opencv-getperspective-transform-example/}
 
